%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Carlos Luna-Pena} \\ \vspace{1pt}
    \small 956-966-0986 $|$ \href{mailto:carlunpen@gmail.com}{\underline{carlunpen@gmail.com}} $|$ 
    \href{https://linkedin.com/in/carlos-luna}{\underline{linkedin.com/in/carlos-luna}} $|$
    \href{https://github.com/clmoon2}{\underline{github.com/clmoon2}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Texas A\&M University}{College Station, TX}
      {Bachelor of Science in Computer Science}{Aug. 2023 -- Present}
      \resumeItemListStart
        \resumeItem{\textbf{Relevant Coursework:} CSCE 331 (Foundations of Software Engineering), CSCE 411 (Design \& Analysis of Algorithms), CSCE 410 (Operating Systems), CSCE 420 (Artificial Intelligence), CSCE 465 (Computer \& Network Security), CSCE 313 (Intro to Computer Systems), Data Structures \& Algorithms.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
  {AI Closet — Team Lead \& ML Engineer}{Sep. 2025 -- Present}
  {Aggies Create (Team Project)}{College Station, TX}
  \resumeItemListStart
    \resumeItem{Built an AI wardrobe assistant with a cross-functional \textbf{Aggies Create} team; owned ML/backend while collaborating on API/UX.}
    \resumeItem{Implemented PyTorch CV boxing/tagging (category/color/pattern) and item embeddings; shipped a \textbf{FastAPI} REST service with a \textbf{Postgres} schema.}
    \resumeItem{Designed the outfit recommender using weather/occasion constraints and a scoring model (color harmony, mood, novelty); iterated via user feedback.}
    \resumeItem{Drove team practices: GitHub PR reviews, issue triage, and weekly sprints with lightweight docs for onboarding.}
  \resumeItemListEnd


    \resumeSubheading
      {HECM Hackathon}{Feb. 2024}
      {Texas A\&M Higher Education Center at McAllen}{McAllen, TX}
      \resumeItemListStart
        \resumeItem{Built a \textbf{Raspberry Pi} + \textbf{6-axis robotic arm} demo with gesture/face/color tracking and control loops; documented a repeatable setup.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
        {\textbf{Aggie Events} $|$ \emph{TypeScript, Next.js, React, Node.js, PostgreSQL, Docker, Google OAuth, GitHub Actions}}{Aug. 2024 -- Present}
        \resumeItemListStart
          \resumeItem{Shipped front-end \textbf{pages \& components} (search, event detail, org views, settings/landing) in \textbf{Next.js + Tailwind} with responsive, accessible UX.}
          \resumeItem{\textbf{Integrated Google OAuth} across frontend/backend; configured secure cookies and \textbf{CORS}; coordinated environment variables.}
          \resumeItem{Worked in a \textbf{monorepo} with \textbf{CI workflows} (lint, type-check, tests) and branch protections to maintain code health.}
          \resumeItem{Extended \textbf{PostgreSQL} schema (events, orgs, likes/views); added indexes and tuned queries.}
        \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{Monee} $|$ \emph{Next.js, React, Node.js, CSV Import, Gemini API (chatbot), Framer}}{TAMUhack 2025}
        \resumeItemListStart
          \resumeItem{Gamified \textbf{financial literacy} app: users complete savings challenges, earn points, and redeem rewards; modern UI with \textbf{Framer} interactions.}
          \resumeItem{Implemented \textbf{CSV transaction} parsing to track spending vs. goals; collaborated on \textbf{Gemini}-powered advice flows.}
          \resumeItem{Partnered on API contracts and server logic; future work includes persistent accounts and a production backend.}
        \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{Studytick} $|$ \emph{Electron, React, SQLite, Electron-Builder}}{2025}
        \resumeItemListStart
          \resumeItem{Built a Windows desktop \textbf{Pomodoro} app with \textbf{Electron + React}; separated main/renderer via a secure \textbf{preload} bridge.}
          \resumeItem{Implemented a \textbf{drift-safe timer} and persisted sessions to \textbf{SQLite}; added charts for streaks and session history.}
          \resumeItem{Packaged installers with \textbf{electron-builder} and auto-update; added settings, notifications, and global hotkeys.}
        \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{Homeworkify} $|$ \emph{JavaScript, Chrome Extension, Python, HTML/CSS}}{Sept. 2023}
        \resumeItemListStart
          \resumeItem{Chrome extension to \textbf{aggregate homework resources} with retry/backoff and a compact UI for quick lookup.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: TypeScript, Java, Python, C/C++, SQL} \\
     \textbf{Frameworks/Libraries}{: React, Next.js, Tailwind, Electron, Node.js} \\
     \textbf{Databases}{: PostgreSQL, SQLite} \\
     \textbf{Tools}{: Docker, Git/GitHub, PyTorch, Linux} \\
     \textbf{Concepts}{: Data Structures \& Algorithms, Operating Systems, OAuth, CORS/rate-limiting}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
