
%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%-------------------------
\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}
% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1
%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubSubheading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & #2 \\
  \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
%-------------------------------------------
%%%%%% RESUME STARTS HERE %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING----------
\begin{center}
    {\LARGE \textbf{Carlos Luna-Pe\~na}} \\ \vspace{2pt}
    College Station, TX \quad $\cdot$ \quad (956) 966-0986 \quad $\cdot$ \quad \href{mailto:carlunpen@gmail.com}{carlunpen@gmail.com} \\ \vspace{2pt}
    \href{https://linkedin.com/in/carlos-luna}{linkedin.com/in/carlos-luna} \quad $\cdot$ \quad \href{https://github.com/clmoon2}{github.com/clmoon2}
\end{center}

%----------SUMMARY----------
\section{Professional Summary}
\resumeSubHeadingListStart
\resumeItem{CS student at Texas A\&M with hands-on experience delivering user-facing web applications and production systems. Skilled in JavaScript, React, HTML, CSS, and modern web frameworks. Proven collaborator in Agile teams, driving accessible UX, code reviews, and rapid iteration.}
\resumeSubHeadingListEnd

%----------EDUCATION----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Texas A\&M University}{College Station, TX}
    {B.S. in Computer Science}{Aug. 2023 -- Present}
\resumeItemListStart
    \resumeItem{Relevant Coursework: Software Engineering, Algorithms, Operating Systems, Artificial Intelligence, Security, Data Structures \\ \& Algorithms}
    \resumeItem{Writing-intensive (W) program: specs, user stories, retrospectives, demos}
\resumeItemListEnd
\resumeSubHeadingListEnd

%----------EXPERIENCE----------
\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {AIPHRODITE (Aggies Create)}{Sep. 2025 -- Present}
    {Team Lead \& ML Engineer}{College Station, TX}
    \resumeItemListStart
        \resumeItem{Led Agile team (standups, sprint planning, PR reviews, onboarding docs) building AI-powered wardrobe assistant web app.}
        \resumeItem{Implemented computer vision tagging (category/color/pattern) and embeddings, served via FastAPI; designed PostgreSQL schema for retrieval and filtering.}
        \resumeItem{Optimized recommender UX (weather/occasion/color harmony); improved click-through by user feedback iteration.}
        \resumeItem{Reduced cycle time and PR rework with rigorous peer review and demo-readiness.}
        \resumeItem{Containerized services; maintained CI pipeline (GitHub Actions) for consistent deployments.}
    \resumeItemListEnd

  \resumeSubheading
    {HECM Hackathon}{Feb. 2024}
    {Participant}{Raspberry Pi + 6-axis Arm}
    \resumeItemListStart
        \resumeItem{Prototyped gesture/face/color tracking demo with real-time control loops; shared reproducible setup and documentation; demoed among peer teams.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%----------PROJECTS----------
\section{Projects}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {Aggie Events (Next.js, React, Tailwind, Node.js, PostgreSQL, Docker, Google OAuth, GitHub Actions)}{Aug. 2024 -- Present}
    \resumeItemListStart
      \resumeItem{Developed responsive UI (search, event detail, org, settings/landing) with accessible, mobile-friendly UX.}
      \resumeItem{Integrated Google OAuth on front- and backend; implemented secure cookies and CORS handling.}
      \resumeItem{Extended PostgreSQL schema (events/orgs/likes/views); improved query performance with indexing and tuning.}
      \resumeItem{Maintained monorepo CI for lint, type-check, and tests; enforced branch protections.}
    \resumeItemListEnd

  \resumeProjectHeading
    {Panda Express POS (CSCE 331 Team Project 2, Agile/Scrum)}{Fall 2025}
    \resumeItemListStart
      \resumeItem{Built RESTful endpoints for inventory, orders, and reporting; implemented role-based access control.}
      \resumeItem{Wrote integration tests to ensure API reliability; containerized services and deployed stable demo versions.}
      \resumeItem{Collaborated in retrospectives and status updates to drive iteration.}
    \resumeItemListEnd

  \resumeProjectHeading
    {Panda Express Mobile App (React Native/Expo, TypeScript)}{Fall 2025}
    \resumeItemListStart
      \resumeItem{Developed ordering/menu/loyalty flows; added push notifications, accessibility features, and offline handling.}
      \resumeItem{Incorporated user study results into iterative improvements.}
    \resumeItemListEnd

  \resumeProjectHeading
    {Personal Web (HTML/CSS/JS)}{2024}
    \resumeItemListStart
      \resumeItem{Created personal portfolio site with semantic HTML, responsive layout, and theme toggling; optimized Lighthouse scores.}
    \resumeItemListEnd

  \resumeProjectHeading
    {Monee (TAMUhack 2025, Next.js, React, CSV Import, Gemini API, Framer)}{2025}
    \resumeItemListStart
      \resumeItem{Built gamified financial literacy app; implemented CSV parsing and chatbot advice flows; delivered polished interactions.}
    \resumeItemListEnd

  \resumeProjectHeading
    {Studytick (Electron, React, SQLite)}{2024}
    \resumeItemListStart
      \resumeItem{Built Pomodoro desktop app with persisted sessions, charts, and auto-update; implemented secure preload bridge.}
    \resumeItemListEnd

  \resumeProjectHeading
    {Aggie Shell (C/C++, Linux)}{2024}
    \resumeItemListStart
      \resumeItem{Implemented Unix shell with multi-stage pipelines, I/O redirection, background jobs, and robust prompt.}
      \resumeItem{Used fork/execvp, pipes, dup2, waitpid (non-blocking), cd/chdir, and tokenizer for command parsing.}
      \resumeItem{Prevented file descriptor leaks and ensured correct stdin restoration.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%----------TECHNICAL SKILLS----------
\section{Technical Skills}
\resumeSubHeadingListStart
\resumeItem{\textbf{Languages:} JavaScript/TypeScript, Java, Python, C/C++, SQL}
\resumeItem{\textbf{Web:} React, Next.js, Tailwind, Node.js/Express, HTML, CSS}
\resumeItem{\textbf{Backend/DevOps:} PostgreSQL, SQLite, Docker, Git/GitHub, GitHub Actions, Linux, Bash}
\resumeItem{\textbf{Auth/Security:} OAuth 2.0, secure cookies, CORS, RBAC}
\resumeItem{\textbf{AI/Automation:} PyTorch, FastAPI, OpenAI API, n8n, Apify}
\resumeItem{\textbf{Systems:} Processes, IPC, fork/execvp, pipes, dup2, waitpid, file I/O}
\resumeItem{\textbf{Practices:} RESTful API design, input validation, accessibility (WCAG), unit/integration testing, CI/CD, Agile/Scrum}
\resumeSubHeadingListEnd

\end{document}
